\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}

\title{three-phase-calendar

A multiplatform modal calendar app for time management\footnote{My thesis, but presented as its heretic, anonymized, and public English edition.}}
\author{Luka Vivi Starr Alice}
\date{08.2024 - ??.2025}
\begin{document}
\maketitle

\begin{abstract}
\textit{One Calendar App to rule them all, One Calendar App to find them; One Calendar App to bring them all and in the darkness bind them.}
\end{abstract}

\section*{Introduction}
In today's world, the field of software engineering has already made many great leaps. A multitude of tooling has allowed people of an insurmountably diverse skill level to enter the IT and Software Development industry, in particular, Web Application Development.

A highly probable direct result of this rapid growth is the popularization of particular software development methodologies, frameworks, libraries, and various other solutions. This phenomenon has caused many, both amateur and enterprise software solutions to commonly encountered problems to end up sharing many similarities in their execution and life-cycle.

The main goal of this project is to challenge the common approaches to a common problem while trying to follow and not violate the well-established software standards and proven best practices.
\section{Project scope and goals}
\section{Technologies used in the development process}
Technologies utilized in both the development and final implementation \& deployment of the project consist of a mixture of the best tools proven for the job and a matter of the developer's preference.
\subsection{EndeavourOS Linux}
\subsection{IDE and text editors}
\subsection{Java 21 (OpenJDK)}
\subsection{PostgreSQL}
\subsection{Docker}
\subsection{Vue.js}
\subsection{Tauri 2.0}
\subsection{Amazon Web Services}
\subsection{Testing tooling}
\section{Implementation and development process}
\section{Deployment and greater picture}
\section*{Summary}
\subsection*{Bibliography}
\subsection*{Index of pictures}

\end{document}